Evolution of solar wind discontinuities in the inner heliosphere

### 2024-05-09 index.qmd
update

- [x] Why ARTEMIS electron data and Wind ion data?
- [ ] Disagreement between anisotropy observed and predicted by the theory

@@

{{< embed notebooks/02_psp_events.ipynb#fig-data-products >}}

@@

@@

>>>>

- [x] Why ARTEMIS electron data and Wind ion data?
- [ ] Disagreement between anisotropy observed and predicted by the theory
  - maybe just too localized anisotropy that is not well measured with available time resolution... 
  - or maybe more complex ion distribution, where nongyrotropy is more important than anisotropy
# TODO

- [ ] Plot Bl(t), jm(l) and ion anisotropy for these cases?

@@

@@

# Alignment

Composition and ionization state should remain invariant.

PSP_ISOIS-EPILO_L2-IC:   Info  Metadata
Parker Solar Probe ISOIS EPI-Lo Level 2 Ion Composition - David McComas (Princeton University)

@@

## Anistropy

@shenComparingPlasmaAnisotropy2024

pressure anisotropy is defined as $Λ = \mu (P_∥ - P_⊥) / B^2$.
